Robust Clustering for Ad Hoc Cognitive Radio Network

### 2017-12-24 journal-draft/ettdoc_JG.tex
change figure captioins and figure

We next consider the robustness of the formed clusters in case that more and more primary users are added to the scenario.
In this case, we increase primary users' activity by adding 20 batches of primary users sequentially in CRN, each batch including 10 primary users which are placed randomly and select a channel at random. 
Figure~\ref{singleton_clusters_100} and \ref{singleton_clusters_200} show the corresponding results for $N=100$ and 200 CR nodes in the scenario.
We basically see that as the primary user activity increases, more unclustered CR nodes result from SOC than the variants of ROSS.
This corrobates a somewhat similar observation of the previous section.
When $N=300$, as shown in Figure~\ref{singleton_clusters_300}, and the amount of newly added primary users is moderate, ROSS-DGA/DFA results in slightly more unclustered CR nodes than SOC, while SOC's performance deteriorates quickly when the number of primary users continues to increase.
Also, Figures~\ref{singleton_clusters_100} to~\ref{singleton_clusters_300} reveal that ROSS with size control mechanism results in significantly less singleton clusters.
\begin{figure*}[t]
\begin{multicols}{3}
    \includegraphics[width=\linewidth]{survival_rate_100_edge50.pdf}\par\caption{Percentage of Unclustered CR nodes when $N=100$}\label{singleton_clusters_100}
    \includegraphics[width=\linewidth]{survival_rate_200_edge50.pdf}\par\caption{Percentage of Unclustered CR nodes when $N=200$}\label{singleton_clusters_200}
    \includegraphics[width=\linewidth]{survival_rate_300_edge50.pdf}\par\caption{Percentage of Unclustered CR nodes when $N=300$}\label{singleton_clusters_300}
\end{multicols}
%\caption{Percentage of CR nodes which are not included in any non-singleton clusters}
%\label{unclustered_100_200_300}
\end{figure*}

@@

We next turn to the size of the formed clusters under the different distributed schemes.
For this we study in Figure~\ref{nClusters_largeNetwork} the average number of total clusters formed under the different schemes for the different parameter combinations considered.
The figure shows that the number of clusters resulting from SOC increases linearly, whereas the number of formed clusters increases sub-linearly in case of the variants of ROSS.
This result coincides with the analysis in Section~\ref{ross_p2_cluster_pruning}.
%When the network becomes denser, more clusters are generated by SOC compared with ROSS variants.
We furthermore consider the empirical distribution function of the size of the formed clusters, for each considered network density, in Figures~\ref{cdf_clusterSize_100}, ~\ref{cdf_clusterSize_200} and~\ref{cdf_clusterSize_300} respectively.
\begin{figure}[!h]
  \centering
   \includegraphics[width=0.7\linewidth]{nClusters_largeNetwork_no_texture.pdf}
  \caption{The number of formed clusters.}
  %, there are $x=6$ when $N=100$, $x=12$ when $N=200$, $x=21$ when $N=300$, which is around $2/3$ of the number of average neighbours.
  \label{nClusters_largeNetwork}
\end{figure}

>>>>

We next consider the robustness of the formed clusters in case that more and more primary users are added to the scenario.
In this case, we increase primary users' activity by adding 20 batches of primary users sequentially in CRN, each batch including 10 primary users which are placed randomly and select a channel at random. 
Figure~\ref{singleton_clusters_100} and \ref{singleton_clusters_200} show the corresponding results for $N=100$ and 200 CR nodes in the scenario.
We basically see that as the primary user activity increases, more unclustered CR nodes result from SOC than the variants of ROSS.
This corrobates a somewhat similar observation of the previous section.
When $N=300$, as shown in Figure~\ref{singleton_clusters_300}, and the amount of newly added primary users is moderate, ROSS-DGA/DFA results in slightly more unclustered CR nodes than SOC, while SOC's performance deteriorates quickly when the number of primary users continues to increase.
Also, Figures~\ref{singleton_clusters_100} to~\ref{singleton_clusters_300} reveal that ROSS with size control mechanism results in significantly less singleton clusters.
\begin{figure*}[t]
\begin{multicols}{3}
    \includegraphics[width=\linewidth]{survival_rate_100_edge50.pdf}\par\caption{Percentage of Unclustered CR nodes with increasing number of PUs, where $N=100$}\label{singleton_clusters_100}
    \includegraphics[width=\linewidth]{survival_rate_200_edge50.pdf}\par\caption{Percentage of Unclustered CR nodes with increasing number of PUs, where $N=200$}\label{singleton_clusters_200}
    \includegraphics[width=\linewidth]{survival_rate_300_edge50.pdf}\par\caption{Percentage of Unclustered CR nodes with increasing number of PUs, where $N=300$}\label{singleton_clusters_300}
\end{multicols}
%\caption{Percentage of CR nodes which are not included in any non-singleton clusters}
%\label{unclustered_100_200_300}
\end{figure*}

@@

We next turn to the size of the formed clusters under the different distributed schemes.
For this we study in Figure~\ref{nClusters_largeNetwork} the average number of total clusters formed under the different schemes for the different parameter combinations considered.
The figure shows that the number of clusters resulting from SOC increases linearly, whereas the number of formed clusters increases sub-linearly in case of the variants of ROSS.
This result coincides with the analysis in Section~\ref{ross_p2_cluster_pruning}.
%When the network becomes denser, more clusters are generated by SOC compared with ROSS variants.
We furthermore consider the empirical distribution function of the size of the formed clusters, for each considered network density, in Figures~\ref{cdf_clusterSize_100}, ~\ref{cdf_clusterSize_200} and~\ref{cdf_clusterSize_300} respectively.
\begin{figure}[!h]
  \centering
   \includegraphics[width=0.7\linewidth]{nClusters_largeNetwork_no_texture.pdf}
  \caption{The number of formed clusters in CRN with different densities.}
  %, there are $x=6$ when $N=100$, $x=12$ when $N=200$, $x=21$ when $N=300$, which is around $2/3$ of the number of average neighbours.
  \label{nClusters_largeNetwork}
\end{figure}
